---
title: "Automatic Collection of Chamber Decisions of the German Federal Constitutional Court"
author: "Sebastian Sternberg"
date: "06/08/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load necessary packages. Scraping is mainly done using rvest. 

```{r}
rm(list = ls())
library(rvest)
library(magrittr)
library(stringr)
require(stringi)
require(dplyr)

```


This extracts all the links to each individual Chamber decision in the first step. These links are then used to extact the information in the second step. This should take around 45 minutes to finish, depending on the sys.sleep chosen.

The starting site:

#https://www.bundesverfassungsgericht.de/SiteGlobals/Forms/Suche/Entscheidungensuche_Formular.html?gtp=5403124_list%253D1&submit=Senden&dateAfter=01.01.1998&dateBefore=31.12.2019&language_=de

7013 links are expected:

Iterate over the link:

```{r}

pages <- c(1:702) # there are 702 pages to scrape (702 pages with each 10 decisions), if search is narrowed down to decisions between 01.01.1998 and 31.12.2019 and language  = German

# getting the links to the decisions
links <- c()
for (i in 1:length(pages)){
  message("Getting decision ", i)
  html <- read_html(paste("https://www.bundesverfassungsgericht.de/SiteGlobals/Forms/Suche/Entscheidungensuche_Formular.html?gtp=5403124_list%253D",
      i, "&submit=Senden&dateAfter=01.01.1998&dateBefore=31.12.2019&language_=de", 
      sep = "")
)
  href <- html %>% html_nodes(".relevance100+a") %>% html_attr("href")
  links <- c(links, href)
  message("taking a break of 1.0 seconds")
  Sys.sleep(1.0)
}

links

save(links, file = "links_decisons.Rda")
```

Now we have the raw links. These need to be cleaned, such that we can call each link in the next step. 

```{r}

# select the decisions' links
decisions <- links[grep("^SharedDocs/Entscheidungen/",links)] %>% strsplit(";") %>% sapply("[", 1)

# the links must look like this: https://www.bundesverfassungsgericht.de/SharedDocs/Entscheidungen/DE/2019/07/rs20190730_2bvr168514.html

#generate the correct link be adding the necessary prefix to it:

decisions <- gsub("SharedDocs/", "https://www.bundesverfassungsgericht.de/SharedDocs/", decisions)

```

In the second step, we want to collect information from the decision texts. For this, we loop over each decision link. On each of these pages with the decision texts, we obtain the required information using the respective html node path. The following shows how this works for one decision:

```{r}

# Testing for one text
case <- read_html("https://www.bundesverfassungsgericht.de/SharedDocs/Entscheidungen/DE/2019/05/qk20190524_1bvq004619.html")

header <- case %>% html_nodes("#navBreadcrumbs strong") %>% html_text()
cite <- case %>% html_nodes(".cite") %>% html_text()
chamber_senate <- case %>% html_nodes(".rr1") %>% html_text()

judge1 <- case %>% html_nodes(".absatz:nth-child(8) span") %>% html_text()
judge2 <- case %>% html_nodes(".absatz:nth-child(9) span") %>% html_text()
judge3 <- case %>% html_nodes(".absatz:nth-child(10) span") %>% html_text()

link_decision <- case %>% html_nodes(".cite a") %>% html_text()

#http://www.residualthoughts.com/2018/03/28/topic-analysis-of-tim-ferris-podcast-using-rvest/

```

Now we do this for all the decisions:

```{r}

list_all <- list()

for(i in 1:length(decisions)){
  
  message("Scraping decision ", i)
  
  case <- read_html(decisions[i])
  
  header <- case %>% html_nodes("#navBreadcrumbs strong") %>% html_text()
  cite <- case %>% html_nodes(".cite") %>% html_text()
  chamber_senate <- case %>% html_nodes(".rr1") %>% html_text() %>% str_c(collapse = " ")
  
judges_names <- case %>% html_nodes(".rr2 span") %>% html_text()
judges_names1 <- case %>% html_nodes(".rr2") %>% html_text() %>% strsplit("\n") %>% unlist() %>% trimws() %>% stri_remove_empty() #some of the names have empty/trailing whitespace which must be first removed to assign the names of the judges correctly

  
  if(length(judges_names) == 0){
    judge1 <- judges_names1[1]
    judge2 <- judges_names1[2]
    judge3 <- judges_names1[3]
    judges_names <- str_c(judges_names1, collapse = " ")
  } else{
    
  judge1 <- judges_names[1]
  judge2 <- judges_names[2]
  judge3 <- judges_names[3]
  judges_names <- str_c(judges_names, collapse = " ")
  }
  if(length(judges_names1) == 0){ #if neither name at html position of judgename and judgename1, write NA
    
    judges_names <- "Not found in header"
    judge1 <- NA
    judge2 <- NA
    judge3 <- NA
  }
  
  
   #if there is no chamber and senate write Not found
  if(length(chamber_senate) == 0){
    chamber_senate <- "Not found"
  }
  
  #get link to decision
  link_decision <- case %>% html_nodes(".cite a") %>% html_text()
  
  #do not extract the aktenzeichen; this can be done via the header later; the reason is that the AZ link is error prone if multiple of them are collected together
  #aktenzeichen <- case %>% html_nodes(".az2 span") %>% html_text()
  #aktenzeichen <- aktenzeichen[1] #extract only the first AZ; this is also the one shown in the link of a decision
  
  list_all[[i]] <-   data.frame(header = header, cite = cite, chamber_senate = chamber_senate, 
                                 judges_names = judges_names,
                                 judge1 = judge1, judge2 = judge2, judge3 = judge3,
                                 link_decision = link_decision)
  
  #Display message
  message("Iteration ", i, " of ", length(decisions),  " successful.")
  message("taking a break")
  Sys.sleep(1.5)
}


df_all_decisions <- do.call("rbind", list_all) #bind them all together in a data frame from the list.


```

This should take around 7176*1.5/60 minutes, depending on how much sys.sleep you choose. 

## Data Cleaning

Clean the decisions. First drop the decisions with an "Urteil", because these are not Chamber decisions

```{r}
source("helper_functions.R")

#load the 

chamber_decisions <- df_all_decisions[!grepl("Urteil", df_all_decisions$header), ]

#some of the remaining ones are a "Beschluss", but also not a chamber decisions. Because we know that sometimes there is a mistake in the citings, we make double sure that we do not drop the wrong decisions by checking whether the word "Kammer" is in the header of the decision and the suggested citation:

chamber_decisions$check_if_chamber1 <- grepl("Kammer", chamber_decisions$cite)
chamber_decisions$check_if_chamber2 <- grepl("Kammer", as.character(chamber_decisions$chamber_senate))

#always true
chamber_decisions$check_if_chamber1 == chamber_decisions$check_if_chamber2

#only keep the decisions which are chamber decisions

chamber_decisions <- chamber_decisions[chamber_decisions$check_if_chamber1 == TRUE, ]

#clean the aktenzeichen

#There are 12 decisions where there is no az in the header. Thus, ifelse is used to replace these with NA such that the
#length matches the nrow of the data.

chamber_decisions$az <- str_extract(chamber_decisions$header, "\\d \\w\\w\\w \\d+...") %>% unlist

# chamber_decisions$az  <- ifelse(is.na(str_extract(chamber_decisions$header, "\\d \\w\\w\\w \\d+...") %>% unlist), NA, str_extract_all(chamber_decisions$header, "\\d \\w\\w\\w \\d+...") %>% unlist)

chamber_decisions <- chamber_decisions %>% select(az, everything())

#create date

for(i in 1:nrow(chamber_decisions)){
  
tmp <-  strsplit(as.character(chamber_decisions$header[i]), " ") %>%  unlist()
chamber_decisions$date[i] <- str_c(tmp[3:5], collapse = " ")

}

chamber_decisions$date <- german_date_to_date(chamber_decisions$date)

#extract the senate the chamber decision was decided in

chamber_decisions$senat <- str_extract(chamber_decisions$az, "[0-9]+") 

chamber_decisions$senat_check <- ifelse(grepl("Ersten Senats", as.character(chamber_decisions$chamber_senate)), 1, NA)

chamber_decisions$senat_check[grepl("Zweiten Senats", as.character(chamber_decisions$chamber_senate))] <- 2

table(chamber_decisions$senat_check, useNA = "ifany")

#There are some mistakes done by the court:

table(chamber_decisions$senat_check == chamber_decisions$senat)

#This is the wrong decision:
#https://www.bundesverfassungsgericht.de/e/rk20090224_1bvr018909.html

#correct this manually:

chamber_decisions$senat[chamber_decisions$az == "2 BvR 189/09"] <- "1"

#check again:
table(chamber_decisions$senat_check == chamber_decisions$senat)

#extract the chambers

chamber_decisions$kammer_cit <- str_extract(as.character(chamber_decisions$cite), "[0-9]+")
chamber_decisions$kammer_txt <- str_extract(as.character(chamber_decisions$chamber_senate), "[0-9]+") 

#check:
table(chamber_decisions$kammer_cit == chamber_decisions$kammer_txt) #there are rare cases where the court makes an error when writing the citation. We will keep track of this later. An example is for instance this decision: http://www.bverfg.de/e/rk20130630_2bvr008513.html

```  


Now we have to take care of the names. This is complex and requires some manual editing. 

```{r}
#extracting the judges names

for(i in 1:nrow(chamber_decisions)){
  
chamber_decisions$richter_txt[i] <- c(names_extract(chamber_decisions$judge1[i]), names_extract(chamber_decisions$judge2[i]),
                                   names_extract(chamber_decisions$judge3[i])) %>% 
                                 str_c(collapse = " ") %>%  
                                  gsub("\\s", ",", .) #to bring it in the form for later analyses

}

#There are some NAs we have to take care off:

chamber_decisions$judges_names[is.na(chamber_decisions$richter_txt)]

#replace the NAs with the judge 1 and judge 2 names and bind strings together:

chamber_decisions$richter_txt[is.na(chamber_decisions$richter_txt)] <- str_c(names_extract(as.character(chamber_decisions$judge1[is.na(chamber_decisions$richter_txt)])),
      names_extract(as.character(chamber_decisions$judge2[is.na(chamber_decisions$richter_txt)])))
  
#check the levels:

unique(levels(as.factor(chamber_decisions$richter_txt)))

#apply second cleaning:

chamber_decisions$richter_txt <- clean_names2(chamber_decisions$richter_txt)

#check the levels again:

unique(levels(as.factor(chamber_decisions$richter_txt)))


####some more checks:

# consolidate richter (from cite)
richter <- clean.names(chamber_decisions$richter_txt)
#richter[richter=="No names in the text"] <- clean.names(case$richter_cit)[richter=="No names in the text"]
richter[richter=="None"] <- NA

# no of richter
nrichter <- unlist(lapply(richter.split(richter), length)) 

table(nrichter)

chamber_decisions$nrichter <- nrichter

#write all problematic cases into vector to check them
test1 <- chamber_decisions$judges_names[chamber_decisions$nrichter != 3] %>% stri_na2empty() %>%  stri_remove_empty()

list_all_names <- c("Baer", "Böckenförde", "Britz", "Broß", "Bryde",
                    "Eichberger", "Gerhardt", "Christ", "DiFabio", "Gaier", "Graßhof",
                    "Grimm", "Haas","Hermanns", "Harbarth", "Hassemer", "Hoffmann-Riem", "Hohmann-Dennhardt",
                    "Hömig", "Huber", "Jaeger", "Jentsch", "Kessal-Wulf", "Kirchhof", "König", "Kruis",
                    "Kühling", "Landau", "Langenfeld", "Limbach", "Lübbe-Wolff", "Maidowski", "Masing",
                    "Mellinghoff", "Müller", "Osterloh", "Ott", "Papier", "Paulus", "Radtke", "Schluckebier",
                    "Seidl", "Sommer", "Steiner", "Voßkuhle", "Winter")

#set the Schreibweise to all names the same: 

list_all_names <- clean.names(list_all_names)
test1 <- clean.names(test1)

#check whether all unique names (important for matching later):
length(list_all_names) == length(unique(list_all_names))

correct_names <- list()

for(i in 1:length(test1)){
  
correct_names[[i]] <- str_c(str_extract_all(test1[i], list_all_names) %>% unlist(), collapse = ",")

}

#The last two are empty (Nothing found), so we have to set them NA to bind the vector the original data frame
correct_names[[61]] <- NA
correct_names[[62]] <- NA

#write into data set:

chamber_decisions$richter_txt[chamber_decisions$nrichter != 3] <- unlist(correct_names)

#now check njudges again:

richter <- clean.names(chamber_decisions$richter_txt)

# no of richter
nrichter <- unlist(lapply(richter.split(richter), length)) 

chamber_decisions$nrichter2 <- nrichter

table(nrichter)

```

There are 3 names which are still wrong (less than 3 judges in a panel). I will add these manually:

No header:

https://www.bundesverfassungsgericht.de/e/rk19990413_2bvr056299.html

```{r}

chamber_decisions$richter_txt[chamber_decisions$nrichter2 != 3] <- c("Hohmann-Dennhardt,Gaier,Kirchhof", "Limbach,Winter,Hassemer", "Limbach,Winter,Hassemer")

#check:
check_names <- str_split(chamber_decisions$richter_txt,",") %>% unlist()

unique(check_names)

#Still trailing whitespace:

#we have to remove them manually; strim or gsub \\s does not work.
check_names <- str_split(chamber_decisions$richter_txt,",") %>% unlist()

chamber_decisions$richter_txt <- gsub(unique(check_names)[33], "Lübbe-Wolff",
                                      chamber_decisions$richter_txt)

chamber_decisions$richter_txt <- gsub(unique(check_names)[34], "Gerhardt",
                                      chamber_decisions$richter_txt)


chamber_decisions$richter_txt <- gsub(unique(check_names)[40], "Hömig",
                                      chamber_decisions$richter_txt)

chamber_decisions$richter_txt <- gsub(unique(check_names)[41], "Bryde",
                                      chamber_decisions$richter_txt)

chamber_decisions$richter_txt <- gsub(unique(check_names)[50], "Jaeger",
                                      chamber_decisions$richter_txt)

chamber_decisions$richter_txt <- gsub(unique(check_names)[51], "Steiner",
                                      chamber_decisions$richter_txt)

chamber_decisions$richter_txt <- gsub(unique(check_names)[53], "Kruis",
                                      chamber_decisions$richter_txt)

chamber_decisions$richter_txt <- gsub(unique(check_names)[54], "Sommer",
                                      chamber_decisions$richter_txt)


#check again:

check_names <- str_split(chamber_decisions$richter_txt,",") %>% unlist()
unique(check_names)

#do we have all names that we manually identified?
length(list_all_names) == length(unique(check_names))

#Finally. Yes we have.

```


```{r}
#some names are still wrong. This is because of inconsistencies on the page of the court: e.g. https://www.bundesverfassungsgericht.de/e/rk20071227_1bvr085306.html . Here, there is an unusual "\n" on the place where the names of the judges appear.

#https://www.bundesverfassungsgericht.de/e/qk20160730_1bvq002916.html repeats the names

#These are the cases where there are formatting errors on the page:

links_formatting_errors <- data.frame(
  aktenzeichen = chamber_decisions$az[grepl("durch", chamber_decisions$richter_txt)], 
                                      header = chamber_decisions$header[grepl("durch", chamber_decisions$richter_txt)], 
                                      link = chamber_decisions$link_decision[grepl("durch", chamber_decisions$richter_txt)])

#write for GFCC:rfG, Urteil des Zweiten Sen

write.csv(links_formatting_errors, "links_formatting_errors.csv")



#######
```


Identify Einstweilige Anordnung (Provisional Orders):
```{r}

#Einstweilige Anordnung:

chamber_decisions$anordnung <- ifelse(grepl("BvQ", chamber_decisions$az), 1, 0)


```

Now we have all the information that we need for the chamber paper. We save the data set. Before, we drop irrelevant information. 

```{r}

chamber_decisions <- chamber_decisions %>% 
  select(az, date, senat, kammer_cit, kammer_txt, richter_txt, anordnung, link = link_decision)

save(chamber_decisions, file = "chamber_decision_cleaned.Rda")

write.csv(chamber_decisions, file = "chamber_decision_cleaned.csv", fileEncoding = "UTF-8")

```


You can of course easily extend this script by scraping additional information, such as how the overall outcome of the case was or who are the plaintiffs etc. 





